---
title: "Mini-Lab-simulation-theta-xbar"
author: "Lane Quigley"
date: "February 6, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE, warning = FALSE)
```

# Introduction

We will investigate the distribution of $\theta$ made so that $\tilde{s}_{12}=0$ (looking only at the first clockwise root solution in radians) and the distribution of $\bar{X}$, the sample mean.

This will be done by simulation.

# Method and tasks

## Function name and parameters

Call the function `xbarthetadist()` make it take arguments `n` the sample size, $iter$ the number of iterations, $\mu$ the population mean vector (2X1) and the var-cov matrix (2X2). You may wish to pass other arguments.

## `theta`

There are various ways to find theta -- the most alegant is to use the analytical solution which is what we will use here.

## Tasks

Make a function that does the following:

1. Repeatedly simulates a sample of size $n$ from a bivariate normal that has mean $\mu$ and variance covariance matrix $\Sigma$. 
2. Uses each sample to calculate $\bar{X}$ and $\theta$
3. Stores these values appropriately
4. Makes a total of 4  plots using `ggplot`: 
  +  scatterplot and 
  +  2d density plot of $\bar{X}$
  +  a histogram  and 
  +  a density plot of $\theta$
  
You may wish to consult <http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/>
  
```{r}
xbarthetadist = function(n,iter,mu,sigma){
  library(mvtnorm)
  library(ggplot2)
  mat = matrix(NA, nr= iter, nc=4)
  colnames(mat)= c("xbar1","xbar2","thetae","thetar")
  for(i in 1:iter){
    x = rmvnorm(n,mu,sigma)
    mat[i,c(1,2)] <- colMeans(x)
    s=(n-1)/n*cov(x)
    eig=eigen(s)
    thetaeigen=acos(eig$vectors[,1][1])
    thetarot= .5*atan(2*s[1,2]/(s[1,1]-s[2,2])) + pi/2
    
    mat[i,3]<-thetaeigen
    mat[i,4]<-thetarot
    


  }

  df=as.data.frame(mat)
  g=ggplot(df, aes(x=xbar1,y=xbar2))  + coord_equal()

  gp = g + geom_point()
  print(gp)
  gd = g + stat_density_2d()
  print(gd)

  gt=ggplot(data=df, aes(df$thetar)) + geom_histogram() + xlab("Theta Value")
  print(gt)

  gt2 = ggplot(data=df, aes(df$thetar)) + geom_density() + xlab("Theta")
  print(gt2)
 # thetaValues = df$theta;
 # hist(thetaValues)
  #plot(density(thetaValues))

  head(mat)
}



```

  
# Run the function

To show the function works execute the following function calls

```{r function, eval=TRUE}
mu1=c(0,0)
sigma1 = matrix(c(100,40,40,200), nr=2,nc=2,byrow=FALSE)
xbarthetadist(n=80,iter=1000,mu=mu1,sigma=sigma1)

sigma2 = matrix(c(100,-40,-40,200), nr=2,nc=2,byrow=FALSE)
xbarthetadist(n=80,iter=1000,mu=mu1,sigma=sigma2)
```

# Now make a Shiny server

Using the shiny dashboard template create widgets to input `n`, `iter`, `mu`, $\sigma_{ij}$ the output will be the plots: 2d density plot of $\bar{X}$ and histogram of $\theta$. I will leave it to you to make the suitable bounds on the widget variables (remember that the covariance matrix is symmetrical)

```{r}

```


